---
output:
  html:
    toc: 
      collapse: subsections
---


# Black Math Achievement

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

```{r Packages, echo=FALSE, message=FALSE, warning=FALSE}

#requires install.packages("pacman")
pacman::p_load(readxl, janitor, tidyverse)

```

```{r Data, echo=FALSE, message=FALSE, warning=FALSE}

##Change order of 'National public' to be last so that is always the same color##

#main
df <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8m_race_eth.csv')

df$Jurisdiction <- factor(df$Jurisdiction,levels = c('Alabama', 'Alaska', 'Arizona', 'Arkansas', 'California', 'Colorado', 'Connecticut', 'Delaware', 'District of Columbia', 'DoDEA', 'Florida', 'Georgia', 'Hawaii', 'Idaho', 'Illinois', 'Indiana', 'Iowa', 'Kansas', 'Kentucky', 'Louisiana', 'Maine', 'Maryland', 'Massachusetts', 'Michigan', 'Minnesota', 'Mississippi', 'Missouri', 'Montana', 'Nebraska', 'Nevada', 'New Hampshire', 'New Jersey', 'New Mexico', 'New York', 'North Carolina', 'North Dakota', 'Ohio', 'Oklahoma', 'Oregon', 'Pennsylvania', 'Puerto Rico', 'Rhode Island', 'South Carolina', 'South Dakota', 'Tennessee', 'Texas', 'Utah', 'Vermont', 'Virginia', 'Washington', 'West Virginia', 'Wisconsin', 'Wyoming', 'National public'))

#nslp
df_nslp <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8m_race_eth_nslp.csv')

df_nslp$Jurisdiction <- factor(df_nslp$Jurisdiction,levels = c('Alabama', 'Alaska', 'Arizona', 'Arkansas', 'California', 'Colorado', 'Connecticut', 'Delaware', 'District of Columbia', 'DoDEA', 'Florida', 'Georgia', 'Hawaii', 'Idaho', 'Illinois', 'Indiana', 'Iowa', 'Kansas', 'Kentucky', 'Louisiana', 'Maine', 'Maryland', 'Massachusetts', 'Michigan', 'Minnesota', 'Mississippi', 'Missouri', 'Montana', 'Nebraska', 'Nevada', 'New Hampshire', 'New Jersey', 'New Mexico', 'New York', 'North Carolina', 'North Dakota', 'Ohio', 'Oklahoma', 'Oregon', 'Pennsylvania', 'Puerto Rico', 'Rhode Island', 'South Carolina', 'South Dakota', 'Tennessee', 'Texas', 'Utah', 'Vermont', 'Virginia', 'Washington', 'West Virginia', 'Wisconsin', 'Wyoming', 'National public'))

#gen
df_gen <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8m_race_eth_gen.csv')

df_gen$Jurisdiction <- factor(df_gen$Jurisdiction,levels = c('Alabama', 'Alaska', 'Arizona', 'Arkansas', 'California', 'Colorado', 'Connecticut', 'Delaware', 'District of Columbia', 'DoDEA', 'Florida', 'Georgia', 'Hawaii', 'Idaho', 'Illinois', 'Indiana', 'Iowa', 'Kansas', 'Kentucky', 'Louisiana', 'Maine', 'Maryland', 'Massachusetts', 'Michigan', 'Minnesota', 'Mississippi', 'Missouri', 'Montana', 'Nebraska', 'Nevada', 'New Hampshire', 'New Jersey', 'New Mexico', 'New York', 'North Carolina', 'North Dakota', 'Ohio', 'Oklahoma', 'Oregon', 'Pennsylvania', 'Puerto Rico', 'Rhode Island', 'South Carolina', 'South Dakota', 'Tennessee', 'Texas', 'Utah', 'Vermont', 'Virginia', 'Washington', 'West Virginia', 'Wisconsin', 'Wyoming', 'National public'))

```

## Alabama {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alabama") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))



```

### Lower Income & Black in Alabama {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alabama") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Alabama {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alabama") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Alaska {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alaska") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Alaska {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alaska") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Alaska {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alaska") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Arizona {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arizona") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Arizona {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arizona") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Arizona {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arizona") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Arkansas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arkansas") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Arkansas {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arkansas") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Arkansas {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arkansas") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## California {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="California") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in California {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="California") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in California {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="California") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Colorado {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Colorado") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Colorado {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Colorado") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Colorado {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Colorado") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Connecticut {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Connecticut") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Connecticut {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Connecticut") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Connecticut {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Connecticut") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Delaware {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Delaware") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Delaware {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Delaware") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Delaware {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Delaware") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Florida {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Florida") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Florida {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Florida") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Florida {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Florida") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Georgia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Georgia") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Georgia {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Georgia") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Georgia {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Georgia") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Hawaii {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Hawaii") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Hawaii {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Hawaii") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Hawaii {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Hawaii") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


## Idaho {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Idaho") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Idaho {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Idaho") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Idaho {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Idaho") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Illinois {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Illinois") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Illinois {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Illinois") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Illinois {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Illinois") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Indiana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Indiana") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Indiana {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Indiana") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Indiana {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Indiana") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Iowa {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Iowa") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Iowa {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Iowa") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Iowa {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Iowa") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Kansas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kansas") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Kansas {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kansas") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Kansas {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kansas") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Kentucky {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kentucky") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Kentucky {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kentucky") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Kentucky {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kentucky") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Louisiana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Louisiana") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Louisiana {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Louisiana") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Louisiana {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Louisiana") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Maine {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maine") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Maine {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maine") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Maine {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maine") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Maryland {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maryland") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Maryland {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maryland") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Maryland {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maryland") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Massachusetts {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Massachusetts") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Massachusetts {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Massachusetts") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Massachusetts {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Massachusetts") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


## Michigan {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Michigan") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Michigan {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Michigan") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Michigan {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Michigan") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Minnesota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Minnesota") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Minnesota {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Minnesota") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Black Boys in Minnesota {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Minnesota") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Mississippi {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Mississippi") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Mississippi {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Mississippi") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Mississippi {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Mississippi") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Missouri {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Missouri") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Missouri {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Missouri") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Missouri {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Missouri") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Montana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Montana") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Montana {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Montana") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Montana {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Montana") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))
```

## Nebraska {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nebraska") %>%
  mutate(Jurisdiction = factor(Jurisdiction, levels = c('Nebraska', 'National public'))) %>% #Changes order of levels
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Nebraska {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nebraska") %>%
  mutate(Jurisdiction = factor(Jurisdiction, levels = c('Nebraska', 'National public'))) %>% #Changes order of levels
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Nebraska {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nebraska") %>%
  mutate(Jurisdiction = factor(Jurisdiction, levels = c('Nebraska', 'National public'))) %>% #Changes order of levels
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Nevada {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nevada") %>%
  mutate(Jurisdiction = factor(Jurisdiction, levels = c('Nevada', 'National public'))) %>% #Changes order of levels
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Nevada {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nevada") %>%
  mutate(Jurisdiction = factor(Jurisdiction, levels = c('Nevada', 'National public'))) %>% #Changes order of levels
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Nevada {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nevada") %>%
   mutate(Jurisdiction = factor(Jurisdiction, levels = c('Nevada', 'National public'))) %>% #Changes order of levels
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## New Hampshire {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Hampshire") %>%
   mutate(Jurisdiction = factor(Jurisdiction, levels = c('New Hampshire', 'National public'))) %>% #Changes order of levels
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in New Hampshire {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Hampshire") %>%
  mutate(Jurisdiction = factor(Jurisdiction, levels = c('New Hampshire', 'National public'))) %>% #Changes order of levels
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in New Hampshire {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Hampshire") %>%
  mutate(Jurisdiction = factor(Jurisdiction, levels = c('New Hampshire', 'National public'))) %>% #Changes order of levels
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## New Jersey {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Jersey") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in New Jersey {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Jersey") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in New Jersey {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Jersey") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## New Mexico {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Mexico") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in New Mexico {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Mexico") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in New Mexico {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Mexico") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## New York {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New York") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in New York {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New York") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in New York {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New York") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## North Carolina {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Carolina") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in North Carolina {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Carolina") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in North Carolina {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Carolina") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## North Dakota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Dakota") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in North Dakota {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Dakota") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in North Dakota {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Dakota") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Ohio {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Ohio") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Ohio {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Ohio") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Ohio {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Ohio") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Oklahoma {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oklahoma") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Oklahoma {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oklahoma") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Oklahoma {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oklahoma") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Oregon {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oregon") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Oregon {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oregon") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Oregon {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oregon") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Pennsylvania {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Pennsylvania") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Pennsylvania {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Pennsylvania") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Pennsylvania {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Pennsylvania") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Rhode Island {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Rhode Island") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Rhode Island {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Rhode Island") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Rhode Island {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Rhode Island") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## South Carolina {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Carolina") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in South Carolina {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Carolina") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in South Carolina {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Carolina") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## South Dakota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Dakota") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in South Dakota {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Dakota") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in South Dakota {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Dakota") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Tennessee {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Tennessee") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Tennessee {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Tennessee") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Tennessee {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Tennessee") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Texas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Texas") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Texas {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Texas") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Texas {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Texas") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Utah {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Utah") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Utah {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Utah") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Utah {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Utah") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Vermont {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Vermont") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Vermont {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Vermont") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Vermont {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Vermont") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Virginia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Virginia") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Virginia {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Virginia") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Virginia {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Virginia") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Washington {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Washington") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Washington {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Washington") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Washington {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Washington") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## West Virginia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="West Virginia") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in West Virginia {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="West Virginia") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in West Virginia {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="West Virginia") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Wisconsin {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wisconsin") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Wisconsin {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wisconsin") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Wisconsin {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wisconsin") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

## Wyoming {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wyoming") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(230, 290) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

### Lower Income & Black in Wyoming {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_nslp %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wyoming") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 280) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```


### Black Boys in Wyoming {.unnumbered}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

df_gen %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wyoming") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(225, 295) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Math") +
    theme(legend.position = "bottom") +   scale_color_discrete(name="") +      scale_color_manual(values=c("#228B22", "black"))


```

