# Data sets

The plots that populate the content of this site are created from the data sets presented on this page. These data are downloaded from the [NAEP Data Explorer](https://www.nationsreportcard.gov/ndecore/landing) and then wrangled into a tidy format.

```{r set global options, echo=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

```{r Packages, echo=FALSE, message=FALSE, warning=FALSE}

#requires install.packages("pacman")
pacman::p_load(readxl, janitor, tidyverse, DT)

```

  
### Black students by National School Lunch Program status (8th grade) {-}
```{r}

math_df <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8m_race_eth_nslp.csv', show_col_types = FALSE) %>% 
  filter(RaceEth=="Black") %>%
  mutate(Subject = "Math")

read_df <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv', show_col_types = FALSE) %>% 
  filter(RaceEth=="Black") %>%
  mutate(Subject = "Reading")
  
merged_df <- rbind(math_df, read_df) %>%
  relocate(Subject, .after = Jurisdiction) %>%
  arrange(Year, Jurisdiction)

merged_df %>%
  datatable(., filter = 'top', rownames = F) %>% 
  DT::formatStyle(columns = colnames(merged_df), fontSize = '75%')

```

  
### Black students by reported gender (8th grade) {-}
```{r}

math_df <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8m_race_eth_gen.csv', show_col_types = FALSE) %>% 
  filter(RaceEth=="Black") %>%
  mutate(Subject = "Math")

read_df <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv', show_col_types = FALSE) %>% 
  filter(RaceEth=="Black") %>%
  mutate(Subject = "Reading")
  
merged_df <- rbind(math_df, read_df) %>%
  relocate(Subject, .after = Jurisdiction) %>%
  arrange(Year, Jurisdiction)

merged_df %>%
  datatable(., filter = 'top', rownames = F) %>% 
  DT::formatStyle(columns = colnames(merged_df), fontSize = '75%')


```

  
### Hispanic students by National School Lunch Program status (8th grade) {-}
```{r}

math_df <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8m_race_eth_nslp.csv', show_col_types = FALSE) %>% 
  filter(RaceEth=="Hispanic") %>%
  mutate(Subject = "Math")

read_df <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv', show_col_types = FALSE) %>% 
  filter(RaceEth=="Hispanic") %>%
  mutate(Subject = "Reading")
  
merged_df <- rbind(math_df, read_df) %>%
  relocate(Subject, .after = Jurisdiction) %>%
  arrange(Year, Jurisdiction)

merged_df %>%
  datatable(., filter = 'top', rownames = F) %>% 
  DT::formatStyle(columns = colnames(merged_df), fontSize = '75%')

```

  
### Hispanic students by reported gender (8th grade) {-}
```{r}

math_df <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8m_race_eth_gen.csv', show_col_types = FALSE) %>% 
  filter(RaceEth=="Hispanic") %>%
  mutate(Subject = "Math")

read_df <- read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv', show_col_types = FALSE) %>% 
  filter(RaceEth=="Hispanic") %>%
  mutate(Subject = "Reading")
  
merged_df <- rbind(math_df, read_df) %>%
  relocate(Subject, .after = Jurisdiction) %>%
  arrange(Year, Jurisdiction)

merged_df %>%
  datatable(., filter = 'top', rownames = F) %>% 
  DT::formatStyle(columns = colnames(merged_df), fontSize = '75%')


```